PAPER TEMPLATE FOR ISMIR 2014

### 2014-04-28 paper/paper.tex
revision to text

In both tasks, we assume that annotations take the form of a partitioning of the track 
into intervals ${(s_i, t_i)}_{i=1}^m$, where $s_0=0$ denotes the beginning of track, 
$t_m$ denotes the end of the track, and $t_i = s_{i+1}$.
Structural annotation additionally requires that each interval be assigned a label $y_i$.

@@

\emph{Boundary detection} measures the precision, recall, and f-measure of boundary prediction within a tolerance window.
Let $B^R$ ($B^E$) denote the set of unique interval boundaries in the reference (estimated) annotation, and let $W$ denote 
a tolerance window, typically either $0.5$s or $3.0$s.  
A \emph{hit} is defined as a pair $b_e \in B^E$, $b_r \in B^R$ such that $|b_e - b_r|
\leq W$.

No estimated boundary is counted as a hit for more than one reference boundary, and vice versa.
This is accomplished by computing a maximum bipartite matching $H_W$ between $B^E$ and $B^R$ (subject to the window constraint $W$) using the Hopcroft-Karp algorithm~\cite{hopcroft1973n}.  
Precision and recall with window $W$ are defined as
\begin{align}
P_W(B^R, B^E) &\defeq \frac{|H_W|}{|B^E|}\\
R_W(B^R, B^E) &\defeq \frac{|H_W|}{|B^R|},
\end{align}
and the corresponding f-measure is defined by taking their harmonic mean.

@@

\subsubsection{Structural annotation}
Two standard methods of evaluating structural annotation accuracy are \emph{pairwise classification}~\cite{levy2008structural}
and conditional entropy~\cite{lukashevich2008towards}.  In both methods, a collection of samples are generated by sampling the
labels at time steps between $0$ and the track duration.  Each sample $x_i$ is assigned a reference label $y_i^R$ and
and estimated label $y_i^E$.  Our implementation follows the MIREX guidelines, and generates samples at a default rate of 10Hz.

In order for annotation metrics to be well-defined, both reference and estimated annotations must span the same duration of time.
This is accomplished in our implementation by trimming or padding the estimated annotation to exactly match the start and end-times
reported in the reference annotation, and synthesizing unique reference labels if necessary.  Note that the reference annotation is
never modified, only the estimated annotations: in this way, comparison of multiple estimations cannot be compromised by an
estimator reporting an incorrect track duration.

Given the labels for the samples $\{(y_i^R, y_i^E)\}_{i=1}^n$, the \emph{pairwise classification} metrics are defined as precision,
recall, and f-measure of label agreement over all unique, distinct pairs $i \neq j$.  
Let $A_R = \{ \{i, j\} \given y_i^R = y_j^R\}$ denote the set of similarly labeled frames in the reference, with $A_E$ defined
analogously for the estimation.  Then the precision and recall are defined simply as
\begin{align}
P_\text{pair} &\defeq \frac{ |A_E \cap A_R| }{ |A_E| }\\
R_\text{pair} &\defeq \frac{ |A_E \cap A_R| }{ |A_R| }.
\end{align}

\emph{Normalized conditional entropy} scores are computed by estimating the conditional entropy of the estimated label $y^E$ given
the reference label $y^R$ and vice versa.  Let $P$ denote the empirical joint distribution over reference and estimated labels:
\begin{align}
P_{ij} &\propto \left|\{t \given y_t^R = i \wedge y_t^E = j\}\right|.
\end{align}
Then the conditional entropies $H(E \given R)$ and $H(R \given E)$ (in bits) are derived from the 
marginals ${p_i^R = \sum_j P_{ij}}$ and ${p_j^E = \sum_i P_{ij}}$ as described by Lukashevich~\cite{lukashevich2008towards}.

>>>>

In both tasks, we assume that annotations express a partitioning of the track 
into intervals ${(s_i, t_i)}_{i=1}^m$, where $s_0=0$ denotes the beginning of track, 
$t_m$ denotes the end of the track, and $t_i = s_{i+1}$.
Structural annotation additionally requires that each interval be assigned a label $y_i$.

@@

\emph{Boundary detection} measures the precision, recall, and F-measure of boundary prediction within a window.
Let $B^R$ ($B^E$) denote the set of unique interval boundaries in the reference (estimated) annotation, and let $W$ denote 
a window, typically either $0.5$s or $3.0$s.  
A \emph{hit} is defined as a pair $b_e \in B^E$, $b_r \in B^R$ such that $|b_e - b_r|
\leq W$.

No estimated boundary is counted as a hit for more than one reference boundary, and vice versa.
This is accomplished by computing a maximum bipartite matching $H_W$ between $B^E$ and $B^R$ (subject to the window constraint $W$)
using the Hopcroft-Karp algorithm~\cite{hopcroft1973n}.  This deviates from the greedy heuristic used in the MIREX
implementation, but it is guaranteed to produce a correct matching.  Precision and recall at window $W$ are defined as
\begin{align}
P_W(B^R, B^E) &\defeq \frac{|H_W|}{|B^E|}\\
R_W(B^R, B^E) &\defeq \frac{|H_W|}{|B^R|},
\end{align}
and the corresponding F-measure is defined by taking their harmonic mean.

@@

\subsubsection{Structural annotation}
Two standard methods of evaluating structural annotation accuracy are \emph{pairwise classification}~\cite{levy2008structural}
and conditional entropy~\cite{lukashevich2008towards}.  In both methods, a collection of samples are generated by sampling the
labels at time steps between $0$ and the track duration.  The $i$th sample is assigned a reference label $y_i^R$ and
and estimated label $y_i^E$.  Our implementation follows the MIREX guidelines, and generates samples at a default rate of 10Hz.

Reference and estimated annotations must span identical time durations for annotation metrics to be well-defined.
This is accomplished in our implementation by trimming or padding the estimated annotation to exactly match the start and end-times
reported in the reference annotation, and synthesizing unique labels if necessary.

Given the labels for the samples $\{(y_i^R, y_i^E)\}_{i=1}^n$, the \emph{pairwise classification} metrics are defined as precision,
recall, and F-measure of label agreement over all unique, distinct pairs $i \neq j$.  
Let $A_R = \{ \{i, j\} \given y_i^R = y_j^R\}$ denote the set of similarly labeled frames in the reference, with $A_E$ defined
analogously for the estimation.  Precision and recall are defined as
\begin{align}
P_\text{pair} &\defeq \frac{ |A_E \cap A_R| }{ |A_E| }\\
R_\text{pair} &\defeq \frac{ |A_E \cap A_R| }{ |A_R| }.
\end{align}

\emph{Normalized conditional entropy} scores are computed by estimating the conditional entropy of the estimated label $y^E$ given
the reference label $y^R$ and vice versa.  Let $P$ denote the empirical joint distribution over reference and estimated labels:
\begin{align}
P_{ij} &\propto \left|\{t \given y_t^R = i \wedge y_t^E = j\}\right|.
\end{align}
Let $Y^R$ and $Y^E$ denote random variables corresponding to the reference and estimated label for an arbitrary sample.
The conditional entropies $H\left(Y^E \given Y^R\right)$ and $H\left(Y^R \given Y^E\right)$ are estimated from the 
empirical marginals ${p_i^R = \sum_j P_{ij}}$ and ${p_j^E = \sum_i P_{ij}}$ as described by 
Lukashevich~\cite{lukashevich2008towards}.
